
```{r include}
library(tidyverse)
library(tidymodels)
library(ggplot2)

```

**1.**

```{r}

Abalone_ <- read.csv("abalone.data")
Abalone_$age <- Abalone_$X15 + 1.5

Abalone <- Abalone_
Abalone <- transform(Abalone_, age= X15 + 1.5)

```

```{r}

distr <- Abalone$age
hist(distr, main= "Distribution of age", xlab= "Abalone age", 
     ylim= c(0,1500), xlim= c(0,35), col= "darksalmon", yaxt= "n")
axis(side= 2, at= seq(0, 1500, by=250), cex.axis= 0.6, las= 1)

```
Most of the abalone in the data set has an age in the range 10-12 years,
the youngest abalone is 2.5 years, and the oldest abalone is 30.5 years.

**2.**

```{r}

set.seed(2022)

Abalone_split <- initial_split(Abalone, prop= 0.80, strata= age)

Abalone_train <- training(Abalone_split)

Abalone_test <- testing(Abalone_split)

```

**3.**

```{r}

Abalone_recipe <- recipe(age ~ M + X0.455 + X0.365 + X0.095 + X0.514 + X0.2245 
                         + X0.101 + X0.15, data= Abalone_train)

summary(Abalone_recipe)

```
```{r}
Abalone_recipe_steps <- Abalone_recipe %>%
  step_impute_mean(all_numeric()) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_center(all_predictors()) %>%
  step_scale(all_predictors()) %>%
  step_nzv(all_predictors())

Abalone_recipe_steps
  
```
```{r}

Abalone_recipe_prep <- prep(Abalone_recipe_steps, training = Abalone_train)
Abalone_recipe_prep

Abalone_recipe_final <- bake(Abalone_recipe_prep, Abalone_train)
Abalone_recipe_final

Abalone_recipe_test <- bake(Abalone_recipe_prep, Abalone_test)
Abalone_recipe_test

```

```{r}

Interaction1 <- lm(age ~ M + X0.2245, data= Abalone)
Interaction1

Interaction2 <- lm(age ~ X0.455 + X0.365, data= Abalone)
Interaction2

Interaction3 <- lm(age ~ X0.2245 + X0.15, data= Abalone)
Interaction3


```

The variable rings is proportional to the age of the abalone, however taking 
it into consideration to predict the age of the abalone can lead to overfitting.
Rings is not exclusive and other variables can alter the final prediction.

**4.**

```{r}

lm_Abalone <- linear_reg() %>%
  set_engine(("lm"))
lm_Abalone

```

**5.**

```{r}

lm_Abaflow<- workflow() %>%
  add_model(lm_Abalone) %>%
  add_recipe(Abalone_recipe)

```

**6.**

```{r}

lm_Abafit <- fit(lm_Abaflow, Abalone_train)

FitModel <- lm(age ~ M + X0.455+ X0.365+ X0.095+ X0.514+ X0.2245 + X0.15, 
               data= Abalone)
summary(FitModel)

Hypothetical <- data.frame(M= c('F'), X0.455= c(0.50), X0.365= c(0.10), 
                           X0.095= c(0.30), X0.514= c(4), X0.2245= c(1), 
                           X0.101= c(2), X0.15= c(1))

predict(FitModel, newdata= Hypothetical)
 
```

The hypothetical abalone is approximately 24 years of age.

```{r}

lm_Abafit %>%
  extract_fit_parsnip() %>%
  tidy()

PredAbalone <- predict(lm_Abafit, new_data= Abalone_train %>% select(-age) )
PredAbalone %>%
  head()

```


**7.**

```{r}

PredAbalone <- bind_cols(PredAbalone, Abalone_train %>% select(age))
PredAbalone %>%
  head()

PredAbalone %>%
  ggplot(aes(x= .pred, y= age)) +
  geom_point(alpha= 0.25) +
  geom_abline(lty= 2) +
  coord_obs_pred()

Abalone_metrics <- metric_set(rsq, rmse, mae)
Abalone_metrics(PredAbalone, truth= age, estimate= .pred)

```

The R^2 value demonstrates that approximately 53.11% of the variance of
dependent variables is explained by the variance of the independent variable.
